EPIWEEK ARIMAX MODELS - Influenza hospitalization data

### 2025-06-23 models_with_logback/ES_EPIWEEK/EPIWEEK.Rmd
update

This function utilizes ensembles and single automatic ARIMAX models which have mean cases by epidemiological weeks over the last 2 years as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

>>>>

This function utilizes ensembles and single automatic ARIMAX models which have mean hospitalizations by epidemiological weeks over the last 2 years as exogenous variables. The function fits on a rolling window of previous 104 weeks for the state under analysis and a rolling windows with the same size with 1 week-lag for the exogenous variables to generate forecasts. It return some metrics that evaluate the performance of the models:target_end_date, abs_error, cases, forecast, 'N_of_models", weighted interval score (WIS), predictive quantiles. The user can choose a  single best automatic ARIMAXs (auto=TRUE), or ensembles of 27 permutations of 0,1,2 pdq's (ES27=TRUE) or 64 permutations of 0,1,2,3 pdq's (ES64=TRUE). The user also chooses the number of weeks ahead for each forecast, and the size of the rolling window which is set as 2 years (104 weeks).

### 2025-06-23 models_without_logback/ES_EPIWEEK/EPIWEEK.Rmd
update

# Loads the ADJACENT states models
source("ES_EPIWEEK.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("EPIWEEK_MODELS_influenza_hospitalization.Rdata")

>>>>

# Loads the ADJACENT states models
source("ES_EPIWEEK_nolog.R", local = TRUE, chdir = TRUE)

@@

```{r}
save.image("EPIWEEK_MODELS_influenza_hospitalization_nolog.Rdata")
